\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{ctex}   %允许中文
\usepackage{graphicx}

\usetheme{Madrid}
\usecolortheme{beaver}

\title{NaviPath \newline\newline Bridging the Gap Between Pathologists and AI}
\author{曲廷锌}
\date{\today}

\begin{document}

\frame{\titlepage}

\section{Introduction}

\begin{frame}{Introduction}
    \begin{itemize}
        \item NaviPath: Empowering Pathologists with AI-driven Navigation.
        \item Pathology is a critical step in cancer diagnosis.
        \item Challenges in digital pathology: High-resolution scans and navigation difficulties.
        \item The need for improvement in pathology scan analysis.
    \end{itemize}
\end{frame}

\section{Challenges in Pathology}

\begin{frame}{Challenges in Pathology}
    \begin{enumerate}
        \item Pathology diagnosis is complex and often involves rare cases.
        \item Pathologists require domain knowledge and AI integration.
        \item Integrating AI into the diagnostic process must not hinder pathologists.
    \end{enumerate}
\end{frame}

\section{Research and Development}

\begin{frame}{Research and Development}
    \begin{itemize}
        \item Collaborated with six doctors from two medical centers.
        \item Focused on mitosis (related to tumor malignancy and patient prognosis).
        \item Summarized three research findings.
    \end{itemize}
\end{frame}

\begin{frame}{Research Findings}
    \begin{enumerate}
        \item Overview before details: Low-resolution scans followed by selection of Regions of Interest (ROIs) at high resolution.
        \item Macro Pattern-based Localization: Pathologists reference macro patterns visible at low magnification to locate ROIs.
        \item High-Power Low-Volume: Pathologists use careful and comprehensive navigation strategies to avoid missing critical pathology patterns.
    \end{enumerate}
\end{frame}

\section{NaviPath Design Components}

\begin{frame}{NaviPath Design Components}
    \begin{enumerate}
        \item Layered AI Recommendations:
        \begin{itemize}
            \item Local Recommend: Quick focus at low magnification.
            \item High-Power Field recommendation: Detailed examination at intermediate magnification.
            \item Cell Recommend: Identifying mitotic cells at the highest resolution.
        \end{itemize}
        \item Personalized Recommendations: Customizable AI suggestions based on pathologists' preferences.
        \item Clue-based Navigation at High Magnification: Quick navigation to remote AI recommendations without manual planning.
    \end{enumerate}
\end{frame}

\section{Validation and Results}

\begin{frame}{Validation and Results}
    \begin{itemize}
        \item Employed 15 medical experts to validate NaviPath.
        \item Results compared to manual navigation:
        \begin{enumerate}
            \item Improved efficiency: Over two times more target pathology patterns (mitosis) observed per unit time.
            \item Increased accuracy in identifying target pathology patterns with higher precision and recall.
            \item Reduced cognitive load and increased confidence among pathologists.
        \end{enumerate}
    \end{itemize}
\end{frame}

\section{Conclusion}

\begin{frame}{Conclusion}
    \begin{itemize}
        \item NaviPath bridges the gap between pathologists and AI, improving cancer diagnosis.
        \item Empowers pathologists with AI-driven navigation.
        \item Enhances efficiency and accuracy in pathology analysis.
        \item Supported by medical experts and well-received for future use.
    \end{itemize}
\end{frame}

\end{document}
